### 2015-06-05 Manuscript/Missing_mammals-draft.tex
Revert 72c8954..d3d9fcc
This rolls back to commit 72c89542624c8b4d63aaf5aff595cfd78b145d25.
Minor edit to intro

A downside of the Total Evidence method is that it requires a lot of data.
One must collect molecular data for living taxa and morphological data for both living and fossil taxa; two types of data that require fairly different technical skills (e.g. molecular sequencing \textit{vs.} anatomical description).
Additionally, large chunks of this data can be difficult, or even impossible, to collect for every taxon present in the analysis.
For example, fossils very rarely have molecular data and incomplete fossil preservation may restrict the amount of morphological data available \citep{sansomfossilization2013}. % NC: Worth metioning fossil preservation here briefly as it is also an issue?
Additionally, since the molecular phylogenetics revolution, it has become less common to collect morphological characters for living taxa when molecular data is available (e.g. in \cite{slaterphylogenetic2013}, only 13\% of the 169 living taxa have coded morphological data).
Unfortunately this missing data can lead to errors in phylogenetic inference; in fact, simulations show that the ability of the Total Evidence method to recover the correct phylogenetic topology decreases when there is a low overlap between morphological data in the living and fossil taxa \citep{GuillermeCooper}, regardless the overall amount of morphological data available for the fossils (or the amount of molecular data available for the living species).
The effect of missing data on topology is greatest when living taxa have few morphological data.
This is because (1) a fossil cannot branch in the correct clade if there is no overlapping morphological data in the clade; and (2) a fossil has a higher probability of branching within a clade with more morphological data available for living taxa, regardless of whether this is the correct clade or not \citep{GuillermeCooper}. 
%This can lead to serious topological errors (see Figure ~\ref{Figure_missing_data_problem}).

@@

% TG: Same for the table, I will do the new table combinations later (need some proper coding since I don't wan't to use illustrator - my first paper 100\% reproducible by copy paste!)
\renewcommand\baselinestretch{1.2}\selectfont
\begin{center}
\input{Table_morpho_taxa_proportion}
\end{center}
\renewcommand\baselinestretch{2}\selectfont

@@

\renewcommand\baselinestretch{1.2}\selectfont
\begin{center}
\input{Table_data_structure}
\end{center}
\renewcommand\baselinestretch{2}\selectfont

>>>>

A downside of the Total Evidence method is that it requires a lot of data.
One must collect molecular data for living taxa and morphological data for both living and fossil taxa; two types of data that require fairly different technical skills (e.g. molecular sequencing \textit{vs.} anatomical description).
Additionally, large chunks of this data can be difficult, or even impossible, to collect for every taxon present in the analysis.
For example, fossils very rarely have molecular data and incomplete fossil preservation (e.g. soft \textit{vs.} hard tissues) may restrict the amount of morphological data available \citep{sansomfossilization2013}. % NC: Worth metioning fossil preservation here briefly as it is also an issue?
Additionally, since the molecular phylogenetics revolution, it has become less common to collect morphological characters for living taxa when molecular data is available (e.g. in \cite{slaterphylogenetic2013}, only 13\% of the 169 living taxa have coded morphological data).
Unfortunately this missing data can lead to errors in phylogenetic inference; in fact, simulations show that the ability of the Total Evidence method to recover the correct phylogenetic topology decreases when there is a low overlap between morphological data in the living and fossil taxa \citep{GuillermeCooper}, regardless the overall amount of morphological data available for the fossils (or the amount of molecular data available for the living species).
The effect of missing data on topology is greatest when living taxa have few morphological data.
This is because (1) a fossil cannot branch in the correct clade if there is no overlapping morphological data in the clade; and (2) a fossil has a higher probability of branching within a clade with more morphological data available for living taxa, regardless of whether this is the correct clade or not \citep{GuillermeCooper}. 
%This can lead to serious topological errors (see Figure ~\ref{Figure_missing_data_problem}).

@@

% TG: Same for the table, I will do the new table combinations later (need some proper coding since I don't wan't to use illustrator - my first paper 100\% reproducible by copy paste!)
\begin{center}
\input{Table_results}
\end{center}

%\renewcommand\baselinestretch{1.2}\selectfont
%\begin{center}
%\input{Table_morpho_taxa_proportion}
%\end{center}
%\renewcommand\baselinestretch{2}\selectfont

@@

%\renewcommand\baselinestretch{1.2}\selectfont
%\begin{center}
%\input{Table_data_structure}
%\end{center}
%\renewcommand\baselinestretch{2}\selectfont
